### 2018-08-29 ms.tex
More intro edits.

Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
The aggregated nature of the data means that each data point does not necessarily contain much information, especially if the case counts are aggregated over a large or heterogenous area.
For example, Sturrock \emph{et al.} use only two covariates due to the lack of information in their data \cite{sturrock2014fine}.

A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
One major barrier to this modelling approach us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.

@@

Here we formulate a joint model that combines aggregated surveillance data and point prevalence surveys of \emph{Plasmodium falciparum}.
We compare the joint model to models fitted with only one type of data.
As case studies we use three countries with good routine surveillance data as well as good coverage of prevalence point surveys.

>>>>

Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
The aggregated of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
For example, Sturrock \emph{et al.} used only two covariates in their model \cite{sturrock2014fine}.
These models are also simply an underrepresented class of models in the statistical literature and statistical software.
Wilson \emph{et al.} \cite{wilson2017pointless} use an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.

A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates.
Furthermore, using two complimentary datasets potentially allows better spatial coverage. 
One major barrier to this modelling approach is that these two data sources are on different scales: point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$.
One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.

@@

Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihood functions for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
